ZCB Pricing

### 2018-07-26 ZCB Pricing .Rmd
CN

implicit <- function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:100, J =seq(0,0.10,0.01),T=1){
  # I = partition of time interval
  # J = partition of short rate variable

@@

xvec <- seq(-0.3,0.6,0.01)
R <- implicit(T=5,J= xvec, I = 1:1250)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
  }
plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)

@@

CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250, J = seq(-0.4,0.6,0.01)){
  # I = partition of time interval
  # J = partition of short rate interval

@@

  pu <- function(j){
    -(alpha -beta*J[j])/(4*dr) - sigma^2/(4*(dr^2)) 
  }

@@

  for (i in 1:(length(I))){

@@

xvec <- seq(-0.4,0.6,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
}
plot(CN(), x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```

```{r 11}
# Modified Fully Implicit Method
```

>>>>

implicit <- function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:1250, J =seq(-0.4,0.6,0.005),T=5){
  # I = partition of time interval
  # J = partition of short rate variable

@@

xvec <- seq(-0.4,0.6,0.005)
R <- implicit(T=5,J= xvec, I = 1:1250)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
  }
plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)

@@

CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250, J = seq(-0.4,0.8,0.005)){
  # I = partition of time interval
  # J = partition of short rate interval

@@

  pu <- function(j){
    -(alpha -beta*J[j])/(4*dr) - sigma^2/(4*(dr^2))

@@

  for (i in I){

@@

xvec <- seq(-0.4,0.8,0.005)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
}
plot(CN(), x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```

```{r 11}
